---
title: "Bracket"
author: "AwesomePie1453"
date: "3/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Part 3

## The Bracket! 

Awesome, now just knit this document/run the code and it will generate the winners. Be sure to fill your bracket out starting in each round with the West region, then the East, then the South, then the Midwest.

```{r library, include=FALSE}
library(rvest)
library(implied)
library(tidyverse)
library(odds.converter)
library(robotstxt)
```


```{r Wprob, includ=FALSE}

Weighted_Probabilities <- function(PT1, team_name_1, PT2, team_name_2){Pbin = (PT1 *100)/(PT1*100 + PT2*100)
gameoutcome <- print(rbinom(1, 1, prob=Pbin))
if(gameoutcome){
  print(paste0(team_name_1," Beats ",team_name_2))
return(c(PT1, team_name_1))
}else{
    print(paste0(team_name_2," Beats ",team_name_1))
return(c(PT2,team_name_2))
}
}
```

### Round of 64 Winners

```{r set, include=FALSE}
Gonzaga <- .199595
Arizona <- .1140543
Kentucky <- .08403998
Kansas <- .07257998
Baylor <- .06141383
Auburn <- .04696352
Duke <- .04435443
Villanova <- 0.03801809
Purdue <- .03801809
Tennessee <- .03070692
Texas_Tech <- .03070692
Iowa <- .02217722
UCLA <- .01947268
Houston <- .01565451
Illinois <- .01209666
Arkansas <- .01209666
Texas <-.01124479
Wisconsin <- .009283486
UConn <- .007904751
San_Diego_State <- .00659818
Michigan <- .00659818
LSU <- .00659818
Saint_Marys <- .005287284
Alabama <- .004668888
Virginia_Tech <- .003972039
North_Carolina <- .003972039
Providence <- .003972039
USC <- .003972039
Loyola_Chicago <- .003972039
Boise_State <- .003972039
Marquette <- .003180796
Ohio_State <-.003180796
Miami_FL <-.003180796
Michigan_State <- .003180796
Indiana <- .003180796
Memphis <- .003180796
Seton_Hall <-.003180796
Colorado_State <- .003180796
San_Fransisco <- .001990972
Davidson <- .001990972
UAB <- .001990972
Wyoming <- .001990972
Rutgers <- .001990972
Chattanooga <- .001990972
Colgate <- .001990972
Vermont <- .001593572
Creighton <- .001593572
TCU <- .001593572
Notre_Dame <- .001593572
Richmond <- .001593572
Iowa_State <- .001593572
SDSU <- .001593572
Murray_State <- .001593572
Georgia_State <- .001593572
Longwood <- .001593572
Bryant <- .001593572
Wright_State <- .001593572
Delaware <- .001593572
Jacksonville_State  <- .001593572
Montana_State <- .001593572
TAMCC <- 001593572
New_Mesico_State <- .001593572
CS_Fullerton <- .001593572
Texas_Southern <- .001593572
Akron <- .001593572
Norfolk_State <- .001593572
Saint_Peters <- .001593572
Yale <- .001593572
```


```{r}

library(TeachingDemos)
library(tidyverse)


char2seed('EricWillLose',set=FALSE) %>%
set.seed()
```

```{r Round64}


W1 <- Weighted_Probabilities(Gonzaga, "Gonzaga", Georgia_State, "Georgia St.")
W2 <- Weighted_Probabilities(Boise_State, "Boise State", Memphis, "Memphis")
W3 <- Weighted_Probabilities(UConn, "UConn", New_Mesico_State, "New Mexico State")
W4 <- Weighted_Probabilities(Arkansas, "Arkansas", Vermont, "Vermont")
W5 <- Weighted_Probabilities(Alabama, "Alabama", Rutgers, "Rutgers")
W6 <- Weighted_Probabilities(Texas_Tech, "Texas Tech", Montana_State, "Montana State")
W7 <- Weighted_Probabilities(Michigan, "Michigan", Davidson, "Davidson")
W8 <- Weighted_Probabilities(Duke, "Duke", CS_Fullerton, "CS Fullerton")
W9 <- Weighted_Probabilities(Baylor, "Baylor", Norfolk_State, "Norfolk State")
W10 <- Weighted_Probabilities(North_Carolina, "University of North Carolina", Marquette, "Marquette")
W11 <- Weighted_Probabilities(Saint_Marys, "St. Marys", Indiana, "Indiana")
W12 <- Weighted_Probabilities(UCLA, "UCLA", Akron, "Akron")
W13 <- Weighted_Probabilities(Texas, "Texas", Virginia_Tech, "Virginia Tech")
W14 <- Weighted_Probabilities(Purdue, "Purdue", Yale, "Yale")
W15 <- Weighted_Probabilities(Murray_State, "Murray State", San_Fransisco, "San Fransisco")
W16 <- Weighted_Probabilities(Kentucky, "Kentucky", Saint_Peters, "Saint Peters")
W17 <- Weighted_Probabilities(Arizona, "Arizona", Bryant, "Bryant")
W18 <- Weighted_Probabilities(Seton_Hall, "Seton Hall", TCU, "TCU")
W19 <- Weighted_Probabilities(Houston, "Houston", UAB, "UAB")
W20 <- Weighted_Probabilities(Illinois, "Illinois", Chattanooga, "Chattanooga")
W21 <- Weighted_Probabilities(Colorado_State, "Colorado State", Michigan, "Michigan")
W22 <- Weighted_Probabilities(Tennessee, "Tennessee", Longwood, "longwood")
W23 <- Weighted_Probabilities(Ohio_State, "Ohio State", Loyola_Chicago, "Loyola Chicago")
W24 <- Weighted_Probabilities(Villanova, "Villanova", Delaware, "Delaware")
W25 <- Weighted_Probabilities(Kansas, "Kansas", Texas_Southern, "Texas Southern")
W26 <- Weighted_Probabilities(San_Diego_State, "San Diego State", Creighton, "Creighton")
W27 <- Weighted_Probabilities(Iowa, "Iowa", Richmond, "Richmond")
W28 <- Weighted_Probabilities(Providence, "Providence", SDSU, "South Dakota State")
W29 <- Weighted_Probabilities(LSU, "LSU", Iowa_State, "Iowa State")
W30 <- Weighted_Probabilities(Wisconsin, "Wisconsin", Colgate, "Colgate")
W31 <- Weighted_Probabilities(USC, "USC", Miami_FL, "Miami Florida")
W32 <- Weighted_Probabilities(Auburn, "Auburn", Jacksonville_State, "Jacksonville State")
```
### Round of 32 Winners

```{r Round32}

W33 <- Weighted_Probabilities(as.numeric(W1[1]), W1[2], as.numeric(W2[1]), W2[2])
W34 <- Weighted_Probabilities(as.numeric(W3[1]), W3[2], as.numeric(W4[1]), W4[2])
W35 <- Weighted_Probabilities(as.numeric(W5[1]), W5[2], as.numeric(W6[1]), W6[2])
W36 <- Weighted_Probabilities(as.numeric(W7[1]), W7[2], as.numeric(W8[1]), W8[2])
W37 <- Weighted_Probabilities(as.numeric(W9[1]), W9[2], as.numeric(W10[1]), W10[2])
W38 <- Weighted_Probabilities(as.numeric(W11[1]), W11[2], as.numeric(W12[1]), W12[2])
W39 <- Weighted_Probabilities(as.numeric(W13[1]), W13[2], as.numeric(W14[1]), W14[2])
W40 <- Weighted_Probabilities(as.numeric(W15[1]), W15[2], as.numeric(W16[1]), W16[2])
W41 <- Weighted_Probabilities(as.numeric(W17[1]), W17[2], as.numeric(W18[1]), W18[2])
W42 <- Weighted_Probabilities(as.numeric(W19[1]), W19[2], as.numeric(W20[1]), W20[2])
W43 <- Weighted_Probabilities(as.numeric(W21[1]), W21[2], as.numeric(W22[1]), W22[2])
W44 <- Weighted_Probabilities(as.numeric(W23[1]), W23[2], as.numeric(W24[1]), W24[2])
W45 <- Weighted_Probabilities(as.numeric(W25[1]), W25[2], as.numeric(W26[1]), W26[2])
W46 <- Weighted_Probabilities(as.numeric(W27[1]), W27[2], as.numeric(W28[1]), W28[2])
W47 <- Weighted_Probabilities(as.numeric(W29[1]), W29[2], as.numeric(W30[1]), W30[2])
W48 <- Weighted_Probabilities(as.numeric(W31[1]), W31[2], as.numeric(W32[1]), W32[2])
```

### Sweet 16 Winners

```{r Sweet16}
W49 <- Weighted_Probabilities(as.numeric(W33[1]), W33[2], as.numeric(W34[1]), W34[2])
W50 <- Weighted_Probabilities(as.numeric(W35[1]), W35[2], as.numeric(W36[1]), W36[2])
W51 <- Weighted_Probabilities(as.numeric(W37[1]), W37[2], as.numeric(W38[1]), W38[2])
W52 <- Weighted_Probabilities(as.numeric(W39[1]), W39[2], as.numeric(W40[1]), W40[2])
W53 <- Weighted_Probabilities(as.numeric(W41[1]), W41[2], as.numeric(W42[1]), W42[2])
W54 <- Weighted_Probabilities(as.numeric(W43[1]), W43[2], as.numeric(W44[1]), W44[2])
W55 <- Weighted_Probabilities(as.numeric(W45[1]), W45[2], as.numeric(W46[1]), W46[2])
W56 <- Weighted_Probabilities(as.numeric(W47[1]), W47[2], as.numeric(W48[1]), W48[2])
```

### Elite 8 Winners

```{r Elite8}
W57 <- Weighted_Probabilities(as.numeric(W49[1]), W49[2], as.numeric(W50[1]), W50[2])
W58 <- Weighted_Probabilities(as.numeric(W51[1]), W51[2], as.numeric(W52[1]), W52[2])
W59 <- Weighted_Probabilities(as.numeric(W53[1]), W53[2], as.numeric(W54[1]), W54[2])
W60 <- Weighted_Probabilities(as.numeric(W55[1]), W55[2], as.numeric(W56[1]), W56[2])
```

### Final Four Winners

```{r Final4}
W61 <- Weighted_Probabilities(as.numeric(W57[1]), W57[2], as.numeric(W58[1]), W58[2])
W62 <- Weighted_Probabilities(as.numeric(W59[1]), W59[2], as.numeric(W60[1]), W60[2])
```

### Championship Winner

```{r Finals}
W63 <- Weighted_Probabilities(as.numeric(W61[1]), W61[2], as.numeric(W62[1]), W62[2])
```


Thanks for using this bracket generator, hope you win!