---
title: "Implied Probabilities"
author: "AwesomePie1453"
date: "3/14/2022"
output: html_document
---

###Introduction

In creating the March Madness randomizer, I had to start small by figuring out the implied probabilties. This first R document is me playing around with the implied odds package, as well as the odds converter package. 
Information about each method of implied probability comes from below
https://cran.r-project.org/web/packages/implied/vignettes/introduction.html

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load}
library(implied)
library(tidyverse)
library(odds.converter)
```

### The Basic Method

First I will set up the decimal odds (from Bovada sportsbook) of several NHL games from March 14th and March 15th 2022. 
This is the basic method. I will do the other methods provided by the link above. 

```{r NHL}
NHL_odds <- rbind(c(2.30, 1.667),
                  c(2.75, 1.476),
                  c(2.30, 1.667),
                  c(1.909, 1.909),
                  c(1.952, 1.87))
colnames(NHL_odds) <- c("Home", "Away")
rownames(NHL_odds) <- c("Coyotes vs Senators", "Ducks vs Rangers", "Islanders vs Capitals", "Penguins vs Predators", "Knights vs Jets")
NHL <- implied_probabilities(NHL_odds)
NHL$probabilities
```

### Margin Weights Proportional to the Odds

```{r WPO} 
NHLWPO <- implied_probabilities(NHL_odds, method ="wpo")
NHLWPO$probabilities
```

### The Odds Ratio Method
```{r OR}
NHLOR <- implied_probabilities(NHL_odds, method ="or")
NHLOR$probabilities
```

### The Power Method

```{r Power}
NHLPower <- implied_probabilities(NHL_odds, method ="power")
NHLPower$probabilities
```

### The Additive Method

```{r Add}
NHLAdd <- implied_probabilities(NHL_odds, method ="additive")
NHLAdd$probabilities
```

### Balanced Books

```{r BB}
NHLBB <- implied_probabilities(NHL_odds, method ="bb")
NHLBB$probabilities
```


If you want to learn about any of these, check the link above!

### Doing the opposite

This next method will allow us to go from probabilities to odds. We will do it with the 'power' method, running our probabilites from that one back

```{r Prob}
NHLProb <- implied_odds(NHLPower$probabilities[], 
                     margin = NHLPower$margin[1], 
                     method = 'power')
NHLProb$odds
```

Almost the exact same as what i had input


#### Odds converters
https://www.rdocumentation.org/packages/odds.converter/versions/1.4.8

In this Portfolio, I also want to get used to the odds converter package. There are many different odds. The most common I use being US odds, and decimal. US odds are my favorite, so lets turn the NHL decimal odds to US.

```{r us}
odds.dec2us(NHL_odds)
```

Much better. Now say you wanted to see what +130 (the odds of coyotes to beat senators) looked like in all other formats. Use the 2all function.


```{r 2all}
odds.us2all(+130)
```
You see the third one listed is "PROB", which is probability. Does this probability match up with any of the methods we used above? They are close, but not really. That is because there is no second value to compare to. Generally, +130 implies 43%, but the books operate slightly differently to make money. Truly. You can use prob2us to transform probabilities into what they should be in American odds, same with decimal.

```{r probus}
odds.prob2us(.4348)
```

Hope you learned some important info about odds converting and implied probabilities! The next R markdown will be web scraping Fanduel to grab odds for our March Madness generator. 