---
title: "Webscraping Fanduel"
author: "AwesomePie1453"
date: "3/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Part 2

In the last R markdown (Implied Probability), we played around with implied probability. This one, we will be webscraping Draftkings to get our March Madness odds, so I don't have to type them all in a matrix like with our NHL odds. 

```{r library}
library(rvest)
library(implied)
library(tidyverse)
library(odds.converter)
library(robotstxt)
```

```{r DK}
paths_allowed("https://sportsbook.draftkings.com/leagues/basketball/88670771?category=team-futures")
DraftKings <- read_html("https://sportsbook.draftkings.com/leagues/basketball/88670771?category=team-futures")
typeof("Draftkings")
```

```{r Names}
Team_Names <- DraftKings %>%
  html_nodes(".sportsbook-outcome-cell__body") %>%
  html_text()
Team_Names
```
```{r Odds}
Odds <- DraftKings %>%
  html_nodes(".default-color") %>%
  html_text() %>%
  as.numeric()
Odds
```
```{r tibble}
MM_Odds <- tibble(
  Team = Team_Names,
  Odds= Odds)
MM_Odds
```
Update- could not get it to work on MGM or DK, so I decided just to make it a matrix. Leaving this here as proof that I tried webscraping. 

```{r MM}
MM_odds <- rbind(c(4.00, 7.00, 9.50, 11.00, 13.0, 17.0, 18.0, 21.0, 21.0, 26.0, 26, 36, 41, 51, 66, 66, 71, 86, 101, 121, 121, 121, 151, 171, 201, 201, 201, 201, 201, 201, 251, 251, 251, 251, 251, 251, 251, 251, 401, 401, 401, 401, 401, 401, 401, 501, 501, 501, 501, 501, 501, 501, 501, 501, 501, 501, 501, 501 ,501, 501, 501, 501, 501, 501, 501, 501, 501, 501))
colnames(MM_odds) <- c("Gonzaga", "Arizona", "Kentucky", "Kansas", "Baylor", "Auburn", "Duke", "Villanova", "Purdue", "Tennessee", "Texas Tech", "Iowa", "UCLA", "Houston", "Illinois", "Arkansas", "Texas", "Wisconsin", "UConn", "San Diego State", "Michigan", "LSU", "Saint Marys", "Albama", "Virginia Tech", "North Carolina", "Providence", "USC", "Loyola Chicago", "Boise State", "Marquette", "Ohio State", "Miami-FL", "Michigan State", "Indiana", "Memphis", "Seton Hall", "Colorado State", "San Fransisco", "Davidson", "UAB", "Wyoming", "Rutgers", "Chattanooga", "Colgate", "Vermont", "Creighton", "TCU", "Notre Dame", "Richmond", "Iowa State", "South Dakota State", "Murray State", "Georgia State", "Longwood", "Bryant", "Wright State", "Delaware", "Jacksonville State", "Montana State", "Texas A&M CC", "New Mexico State", "CS Fullerton", "Texas Southern", "Akron", "Norfolk State", "Saint Peters", "Yale")
MM <- implied_probabilities(MM_odds)
MM$probabilities
```

```{r MM2}
MM2_odds <- cbind(c(4.00, 7.00, 9.50, 11.00, 13.0, 17.0, 18.0, 21.0, 21.0, 26.0, 26, 36, 41, 51, 66, 66, 71, 86, 101, 121, 121, 121, 151, 171, 201, 201, 201, 201, 201, 201, 251, 251, 251, 251, 251, 251, 251, 251, 401, 401, 401, 401, 401, 401, 401, 501, 501, 501, 501, 501, 501, 501, 501, 501, 501, 501, 501, 501 ,501, 501, 501, 501, 501, 501, 501, 501, 501, 501))
rownames(MM2_odds) <- c("Gonzaga", "Arizona", "Kentucky", "Kansas", "Baylor", "Auburn", "Duke", "Villanova", "Purdue", "Tennessee", "Texas Tech", "Iowa", "UCLA", "Houston", "Illinois", "Arkansas", "Texas", "Wisconsin", "UConn", "San Diego State", "Michigan", "LSU", "Saint Marys", "Albama", "Virginia Tech", "North Carolina", "Providence", "USC", "Loyola Chicago", "Boise State", "Marquette", "Ohio State", "Miami-FL", "Michigan State", "Indiana", "Memphis", "Seton Hall", "Colorado State", "San Fransisco", "Davidson", "UAB", "Wyoming", "Rutgers", "Chattanooga", "Colgate", "Vermont", "Creighton", "TCU", "Notre Dame", "Richmond", "Iowa State", "South Dakota State", "Murray State", "Georgia State", "Longwood", "Bryant", "Wright State", "Delaware", "Jacksonville State", "Montana State", "Texas A&M CC", "New Mexico State", "CS Fullerton", "Texas Southern", "Akron", "Norfolk State", "Saint Peters", "Yale")
MM2 <- implied_probabilities(MM_odds)
MM2$probabilities
```




Those are the probabilities! And now lets transform the Decimal odds to American. 

```{r US}
odds.dec2us(MM_odds)
```

Dataframe -

```{r oddsdf}
Odds_df <- data_frame(team_name = colnames(MM_odds), odds = MM2_odds)
```


